A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-06-14 methodology.tex
Path --> Ident in fig
why 3 paths but 2 modified args, explanation added

    \draw (13.5,-2.5) node[fill=purple!20](g1){ItemFn};
    \draw (13.5,-3.5) node[fill=purple!20](g2){Local};
    \draw (13.5,-4.5) node[fill=purple!20](g3){ExprCall};
    \draw (13.5,-5.5) node[fill=purple!20](g4){ExprMethodCall};
    \draw (13.5,-6.5) node[fill=purple!20](g5){Path};
    \draw (13.5,-7.5) node[fill=purple!20](g6){clone};
    \node[draw=none, color=purple] at (13.5,-8.3) {Path 3};

@@

Note that the tree depicted in Figure~\ref{fig:extraction} is not an AST; rather, it represents an ASTDiff. The number of paths in the ASTDiff does not directly correspond to the number of changed elements in the source code. Instead, it is determined by the structural differences between the two ASTs of the code versions. The paths in the ASTDiff capture the changes in the code structure between the two versions, allowing us to analyze and extract relevant information for further processing.

>>>>

    \draw (13.5,-2.5) node[fill=purple!20](g1){ItemFn};
    \draw (13.5,-3.5) node[fill=purple!20](g2){Local};
    \draw (13.5,-4.5) node[fill=purple!20](g3){ExprCall};
    \draw (13.5,-5.5) node[fill=purple!20](g4){ExprMethodCall};
    \draw (13.5,-6.5) node[fill=purple!20](g5){Ident};
    \draw (13.5,-7.5) node[fill=purple!20](g6){clone};
    \node[draw=none, color=purple] at (13.5,-8.3) {Path 3};

@@

Note that the tree depicted in Figure~\ref{fig:extraction} is not an AST; rather, it represents an ASTDiff. The number of paths in the ASTDiff does not directly correspond to the number of changed elements in the source code. Instead, it is determined by the structural differences between the two ASTs of the code versions. For example, in Figure~\ref{fig:extraction} we add a \verb+&+ borrow operator to the variable \verb+tail+ and it introduces a new parent node (\verb+ExprReference+) for \verb+tail+. We also add a \verb+clone()+ method call, which modifies the \verb+head+ node and also adds a new sibling node for \verb+head+ to represent the \verb+clone()+. Among the terminals, we only keep \verb+clone+ in our paths, as it is a BC-related keyword. This is why we observe three paths in the ASTDiff, even though only two arguments have been modified. The paths in the ASTDiff capture the changes in the code structure between the two versions, allowing us to analyze and extract relevant information for further processing.
